Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and attentional function: A cross-sectional study based on the parametric g-formula

### 2024-07-24 output/paper/_figures.qmd
Comments from MV before submission.

obj1 <- tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj1)
```
**Marginal contrasts on the logarithmic scale for the effect of a increase from the 10th to the 90th percentile of the {{< acr edcs first_use=true >}} on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020].
:::

@@

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = c(
    "cortisol production",
    "cortisone production",
    "corticosterone production"
  ),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```
**Marginal contrasts on the logarithmic scale for the effect of a increase from the 10th to the 90th percentile of the {{< acr edcs first_use=true >}} on the glucocorticosteroids expressed in ng/ml (HELIX subcohort; 2013-2016).** 
Circles, triangles, and squares indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020].
:::

@@

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5, is_cortisol = TRUE)
```
**Marginal contrasts on the logarithmic scale for the effect of a increase from the 10th to the 90th percentile of the glucocorticosteroids on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020]. Abbreviations: cortisone production (cortisone prod.); cortisol production (cortisol prod.); corticost. prod. (corticosterone production).
:::

>>>>

obj1 <- tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj1)
```
**Marginal contrasts on the logarithmic scale for the effect of an increase from the 10th to the 90th percentile of the {{< acr edcs first_use=true >}} on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020].
:::

@@

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = c(
    "cortisol production",
    "cortisone production",
    "corticosterone production"
  ),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```
**Marginal contrasts on the logarithmic scale for the effect of an increase from the 10th to the 90th percentile of the {{< acr edcs first_use=true >}} on the glucocorticosteroids expressed in ng/ml (HELIX subcohort; 2013-2016).** 
Circles, triangles, and squares indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020].
:::

@@

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5, is_cortisol = TRUE)
```
**Marginal contrasts on the logarithmic scale for the effect of an increase from the 10th to the 90th percentile of the glucocorticosteroids on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020]. Abbreviations: cortisone production (cortisone prod.); cortisol production (cortisol prod.); corticost. prod. (corticosterone production).
:::

### 2024-07-24 output/paper/_tables.qmd
Comments from MV before submission.

dplyr::bind_cols(t1$`_data`, t2$`_data`) |>
  dplyr::select(-`class...4`, -`variable...5`) |>
  dplyr::rename(
    class = "class...1",
    variable = "variable...2"
  ) |>
  dplyr::left_join(
    edcs,
    by = c("variable" = "chem_id")
  ) |>
  dplyr::select(-variable) |>
  dplyr::rename(variable = "short_name") |>
  gt::gt(
    rowname_col = "variable",
    groupname_col = "class"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  ) |>
  gt::tab_footnote(
    footnote = "Estimate and 95% CI.",
    locations = gt::cells_column_labels()
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Pairwise differences between marginal contrasts on the logarithmic scale of males and females, for the effect of a increase from the 10th to the 90th percentile of {{< acr edcs first_use=true >}} on {{< acr hitrtse first_use=true >}}, expressed in {{< acr mss >}}, and on the glucocorticosteroids, expressed in ng/ml (HELIX subcohort; 2013-2016).**
:::

::: {#tbl-hypothesis-3}
```{r hypothesis-3}
tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between marginal contrasts on the logarithmic scale of males and females, for the effect of a increase from the 10th to the 90th percentile of the glucocorticosteroids on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).**
:::

>>>>

dplyr::bind_cols(t1$`_data`, t2$`_data`) |>
  dplyr::select(-`class...4`, -`variable...5`) |>
  dplyr::rename(
    class = "class...1",
    variable = "variable...2"
  ) |>
  dplyr::left_join(
    edcs,
    by = c("variable" = "chem_id")
  ) |>
  dplyr::select(-variable) |>
  dplyr::rename(variable = "short_name") |>
  gt::gt(
    rowname_col = "variable",
    groupname_col = "class"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  ) |>
  gt::tab_footnote(
    footnote = "Estimate and 95% CI.",
    locations = gt::cells_column_labels()
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Pairwise differences between marginal contrasts on the logarithmic scale of males and females, for the effect of an increase from the 10th to the 90th percentile of {{< acr edcs first_use=true >}} on {{< acr hitrtse first_use=true >}}, expressed in {{< acr mss >}}, and on the glucocorticosteroids, expressed in ng/ml (HELIX subcohort; 2013-2016).**
:::

::: {#tbl-hypothesis-3}
```{r hypothesis-3}
tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between marginal contrasts on the logarithmic scale of males and females, for the effect of an increase from the 10th to the 90th percentile of the glucocorticosteroids on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).**
:::
